---
title: "coding_exercise"
output: html_document
---

```{r}
source("setup.R")
```
```{r}
data("knz_bison")
```

# 1. Create a new column in the bison dataset that calculates the individual’s age at the time of observation.
```{r}
knz_bison_age_at_obs <- knz_bison %>% mutate(age_at_obs = rec_year - animal_yob)
print(knz_bison_age_at_obs)
```

# 2. Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).
```{r}
bison_weight <- function(weight_threshold) {
  knz_bison %>%
    filter(animal_weight < weight_threshold)
}
  
  bison_weight(900)
  
```

# 3. Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.

There does appear to be a significant different in weight between male and female bison based on the significant p value of 6.95e-05. Female bison tend to weigh more than males.	
```{r}
ggplot(knz_bison, aes(x = animal_sex, y = animal_weight, fill = animal_sex)) +
  geom_boxplot() +
  labs(
    title = "Bison Weight Distribution by Sex",
    x = "Sex",
    y = "Weight (kg)"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

knz_bison %>% 
  levene_test(animal_weight ~ animal_sex)

knz_bison %>%  
  t_test(animal_weight ~ animal_sex, var.equal = FALSE, detailed = TRUE)
```

